Automated topic naming to support analysis of software maintenance activities

### 2010-08-20 icse/icse2011.tex
finished visualization analysis

For MySQL (Fig. \ref{fig:mysql-timeline}), we similarly validated our NFR patterns with external mailing list data. This release of MySQL was the first to be licenced under the GPL. Version 3.23.31 (January, 2001) was the production release (non-beta), and we see a flurry of topics labeled with \emph{functionality} and \emph{maintainability}, as one might expect. After this point, we can consider this version to have entered the maintenance phase of the lifecycle.

%Note that MySQL's release process was haphazard at this point: they would release a patch version whenever the need arose. By version 5.1, the company moved to a milestone release, with new releases targeted for every six months.

% \todo[inline]{Does our visualization capture the entire timeline?}

%\todo[inline]{try to pin down these reasons below}

>>>>

For MySQL (Fig. \ref{fig:mysql-timeline}), we similarly validated our NFR patterns with external mailing list data. This release of MySQL was the first to be licenced under the GPL. Version 3.23.31 (January, 2001) was the production release (non-beta), and we see a flurry of topics labeled with \emph{functionality} and \emph{maintainability}, as one might expect. After this point, this version enters the maintenance phase of the lifecycle. In May 2001, there is an increase in the number of topics labelled with \emph{portability}. This might be related to release 3.23.38, which focused on Windows compatibility. Similarly, in Augsut, 2002, both \emph{functionality} and \emph{portability} are high in our tool, and mailing list data suggests this is related to the release of version 3.23.52, a general bug fix with focus on security (encoded as the \emph{functionality} NFR in the ISO9126 model). After this point, efforts shift to the newer releases (4.0, 4.1, 5.0).
